Efficient Coalition Formation for Web Services

### 2013-03-10 papers/coalition/coalition.tex
Changes

\emph{Proposition: } The folowwing statement is equivalent with convex condition of equation \ref{eq:convex}.
\\
\\
For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}

\emph{Proof: }

@@

We know $T \subseteq N - \left\{i\right\}$, therefore:

\begin{equation*}
(S \cup \left\{i\right\}) \cap T = T \cup S
\end{equation*}

and we have $S \subseteq T$, therefor:

\begin{equation*}
(S \cup \left\{i\right\}) \cap T = S
\end{equation*}

With a variable chnage of S we have:

\begin{gather*}
v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
\\
\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
\\
\rightarrow v(S^\prime) + V(T) \leq v(S^\prime) + v(S^\prime \cap T)
\end{gather*}

@@

As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our data set and form random coalitions consisting of 3 to 25 web services. We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core. We set $\epsilon$ to a ratio of total payoff of coalition v(C) from 0 to 1. The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.

>>>>

%\ref{eq:convex}.

\emph{Proposition: } A game with characterestic function v is convex \emph{if and only if for all S, T, and i where} $S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$, 
%For $\forall S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N$ we have:
\begin{equation}\label{eq:convex_snow}
v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)
\end{equation}

\emph{Proof. ``only if''} direction,

@@

Considering $S \subseteq T$:

\begin{gather*}
S \cup \left\{i\right\} = (S \cup \left\{i\right\}) \cup T
\\
T = (S \cup \left\{i\right\}) \cap T
\end{gather*}

By setting $A = S \cup \left\{i\right\}$ and $B = T$ we have:

\begin{gather*}
v(S \cup \left\{i\right\}) + v(T) \leq v (T \cup \left\{i\right\}) + v(S)
\\
\rightarrow v(S \cup \left\{i\right\}) + v(T) \leq v((S \cup \left\{i\right\}) \cup T) + v((S \cup \left\{i\right\}) \cap T)
\\
\rightarrow v(A) + V(B) \leq v(A \cup B) + v(A \cap B)
\end{gather*}

For prove of ``if'' direction, for all $A, B \subset N$,

\begin{gather*}
v(A) - v(A \cap B) \leq v(A \cup B) - v(B)
\end{gather*}

By setting $S \cup \left\{i\right\} = A$ and $R = B$ where $S \subseteq R$:

\begin{gather*}
v(S \cup \left\{i\right\}) - v((S \cup \left\{i\right\}) \cap T) \leq v(T \cup (S \cup \left\{i\right\})) - v(T)
\\
\rightarrow v(S \cup \left\{i\right\}) - v(S) \leq v(T \cup \left\{i\right\}) - v(T)
\end{gather*}

@@

As mentioned in preliminaries section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of $\epsilon-Core$ was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our data set and form random coalitions consisting of 3 to 25 web services. We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute least-core. We set $\epsilon$ to a ratio of total payoff of coalition v(C) between 0 and 1. The results in figure \ref{f_leastcore} show, almost in 10\% of random web service coalitions have non-empty core solution and least-core solution is always non-empty letting agents gain only 30\% more by deviating.
